Effects of the body force on the evacuation dynamics

### 2019-12-31 paper.tex
hice algunas correcciones de estilo

Fig. \ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity. The evacuation time was defined as the time until 70\% of the pedestrians left the room. The different markers correspond to different $k$ values ($i.e$ different body ``stiffness''). The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM). The down triangles correspond to an intermediate value between the empirical value presented in Ref... and the chosen by Helbing in Ref...\\

@@

Network analysis is a set of techniques that characterize the structures in a graph. We defined the graph of contacts among individuals. In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\

@@

Fig.~\ref{overlap_vd} shows the overlap as a function of $v_d$. The overlap is defined as $d_{ij}-r_{ij}$ where $d_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles. In the range $v_d \geq 2$~m/s we can see that increasing $v_d$ increases the overlap (for all the $k$ values studied). For a given $v_d$, the overlap increases as the $k$ value decreases. Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.\\

@@

In Fig ... we show the flow as a function of the global density (fundamental diagram). \ref{flow_density_no_body_force} corresponds to non body force ($i.e k_n=0$), \label{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5. Each curve correspond to a different friction value. The circles correspond to the value of the original SFM ($\\kappa = 2.4~E5$), the "+" symbol correspond to the original value increased by a factor of five and triangles correspond to the original value increased by a factor of ten. \\

@@

It is worth mentioning that increasing the body force reduces the flow, for a given density and a given friction value (compare \ref{flow_density_no_body_force} with \ref{flow_density_body_force} ). In other words, pedestrians walk slower along the corridor if the $k$ value increases ($i.e$ if they are stiffer). This result is the opposite of what we get in bottleneck geometry since the stiffer the pedestrians the faster they walk.\\

@@

One way to analyze the clusterization is by creating a network out of the (x,y) positions of the pedestrians. In this network, each node represents a pedestrian and there is a link between a pair of nodes $i,j$ if the pair of pedestrians represented by the nodes are touching each other ($i.e. d_{ij} \leq R_{ij}$). Once the network is created, it is possible to use the analytical tools that allow describing the configuration such as the mean degree, the distribution of clusters, the shortest path length, etc.\\

@@

The mean overlap increases as the global density increases (see Fig...) and the higher the stiffness the lower the overlap. This result is similar to the overlap vs. the desired velocity obtained for bottleneck geometry. The higher the value of $k$ the higher the repulsion of pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\

@@

As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck and increases the mean degree in a corridor. In fig. ... it shown the network associated with the corridor at a particular timestep ($t=$) and a particular global density. Fig. ... corresponds to $k=0$ while Fig. ... corresponds to $k=1.2$~E5. This is an example to show how increasing the stiffness increases the number of contacts between pedestrians. Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$. \\

>>>>

Fig. \ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity. The evacuation time was defined as the time until 70\% of the pedestrians left the room. The different markers correspond to different $k$ values (\textit{i.e.} different body ``stiffness''). The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM). The down triangles correspond to an intermediate value between the empirical value presented in Ref... and the chosen by Helbing in Ref...\\

@@

Network analysis is a set of techniques that characterize the structures in a graph. We defined the graph of contacts among individuals. In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact (\textit{i.e.} $r_{ij}<R{ij}$).\\

@@

Fig.~\ref{overlap_vd} shows the overlap as a function of $v_d$. The overlap is defined as $R_{ij}-r_{ij}$ where $R_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles. In the range $v_d \geq 2$~m/s we can see that increasing $v_d$ increases the overlap (for all the $k$ values studied). For a given $v_d$, the overlap increases as the $k$ value decreases. Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.\\

@@

In Fig. \ref{flow_density} we show the flow as a function of the global density (fundamental diagram). \ref{flow_density_no_body_force} corresponds to non body force (\textit{i.e.} $k_n=0$), \label{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5. Each curve correspond to a different friction value. The circles correspond to the value of the original SFM ($\kappa = 2.4$~E5), the "+" symbol correspond to the original value increased by a factor of five and triangles correspond to the original value increased by a factor of ten. \\

@@

It is worth mentioning that increasing the body force reduces the flow, for a given density and a given friction value (compare \ref{flow_density_no_body_force} with \ref{flow_density_body_force} ). In other words, pedestrians walk slower along the corridor if the $k$ value increases (\textit{i.e.} if they are stiffer). This result is the opposite of what we get in bottleneck geometry since the stiffer the pedestrians the faster they walk.\\

@@

One way to analyze the clusterization is by creating a network out of the (x,y) positions of the pedestrians. In this network, each node represents a pedestrian and there is a link between a pair of nodes $i,j$ if the pair of pedestrians represented by the nodes are touching each other (\textit{i.e.} $r_{ij} \leq R_{ij}$). Once the network is created, it is possible to use the analytical tools that allow describing the configuration such as the mean degree, the distribution of clusters, the shortest path length, etc.\\

@@

The mean overlap increases as the global density increases (see Fig. \ref{overlap_dens}) and the higher the stiffness the lower the overlap. This result is similar to the overlap vs. the desired velocity obtained for bottleneck geometry. The higher the value of $k$ the higher the repulsion of pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\

@@

As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck but increases the mean degree in a corridor. In Fig.\ref{network_corridor} it shown the network associated with the corridor at a particular timestep and a particular global density. Fig. \ref{network_d6_kn0} corresponds to $k=0$ while Fig. \ref{network_d6_knE5} corresponds to $k=1.2$~E5. This is an example to show how increasing the stiffness increases the number of contacts between pedestrians. Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$. \\
